Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-08 paper/paper.Rmd
bayes plot updates

tstatDF <- d %>%
  filter(original_t_stat != "NA") %>%
  select(project_key, replicated_TA_factor, first_author_name, original_t_stat, original_t_df, rep_t_stat, rep_t_df) %>%
  rowwise() %>%
  mutate(origBF = getBF(original_t_stat, original_t_df)) %>%
  rowwise() %>%
  mutate(repBF = getBF(rep_t_stat, rep_t_df), 
         t_ratio = rep_t_df/original_t_df)

@@

ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = t_ratio, 
                             col = replicated_TA_factor)) +
  geom_abline(slope = 1, lty = 2) + 
  geom_smooth(method = "lm", se=FALSE) + 
  geom_text_repel(aes(label = first_author_name), size = 3) + 
  xlab("Original Bayes Factor") + 
  ylab("Replication Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1/3, 3, 10, 100, 100000),
                labels = c("1/10", "1/3", "3", "10","100", "1,000,000")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1/3, 3, 10, 100, 100000),
                labels = c("1/10", "1/3", "3", "10","100", "1,000,000")) + 
  scale_size_continuous(name = "Ratio of replication to original t value") + 
  scale_color_solarized(name = "Subjective replication rating") + 
  theme_bw() +
  theme(legend.position="bottom")
```

>>>>

tstatDF <- d %>%
  filter(original_t_stat != "NA") %>%
  select(project_key, replicated_TA_factor, first_author_name, original_t_stat, original_t_df, rep_t_stat, rep_t_df) %>%
  rowwise() %>%
  mutate(origBF = getBF(original_t_stat, original_t_df)) %>%
  rowwise() %>%
  mutate(repBF = getBF(rep_t_stat, rep_t_df), 
         df_ratio = rep_t_df/original_t_df)

@@

ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = df_ratio, 
                             col = replicated_TA_factor)) +
  geom_abline(slope = 1, lty = 2) + 
  geom_smooth(method = "lm", se=FALSE) + 
  # geom_smooth(data = filter(tstatDF, 
  #                           !(first_author_name %in% c("Atir","Ko"))), 
  #                           method = "lm", se=FALSE, lty = 2, size = .5) + 
  geom_text_repel(aes(label = first_author_name), size = 3) + 
  xlab("Original Bayes Factor") + 
  ylab("Replication Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1/3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c("1/10", "1/3", "3", "10","100", "1,000", 
                           "1,000,000","1,000,000,000")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1/3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c("1/10", "1/3", "3", "10","100", "1,000", 
                           "1,000,000","1,000,000,000")) + 
  scale_size_continuous(name = "Ratio of replication df to original df") + 
  scale_color_solarized(name = "Subjective replication rating") + 
  theme_bw() +
  theme(legend.position="bottom")

# note: fix slope on trend line, because the atir finding is a hack right now so it fits in the axes. 
```
